A weakly structured stem for human origins in Africa

### 2022-08-04 paper.tex
Update paper.tex

We quantify several migration rates among populations after their divergence ~120ka. 
All models infer relatively high gene flow between Ethiopia and western Africa
($m\approx2\times10^{-4},$ the constant proportion of migrant lineages per generation over 60ka).
We further find that Back-to-Africa gene flow at the beginning of the Holocene primarily
affected the ancestors of the Ethiopian agricultural populations, comprising
over half of their genetic ancestry, estimated to be 64--65\%. 
We observe significant gene flow from the Amhara and Oromo into the Nama, a signal which is likely a proxy for the movement of
eastern African caprid and cattle pastoralists \citep{Henn2008-xo,Breton2014-xb}, here estimated to constitute a 25\% ancestry
contribution 2,000 ya. While this gene flow is not apparent from the ADMIXTURE plot (Figure~\ref{fig:diversity}), the ancestry is likely grouped into the Khoe-San component which has drifted appreciably from its ancestry Eastern African source. Colonial period admixture from Europeans into the Nama
was estimated at 15\%, similar to proportions suggested by \texttt{ADMIXTURE}
(Figure~\ref{fig:diversity}).

>>>>

We quantify migration rates among populations after their divergence ~120ka.
Migration, prior to the Bantu expansion, between the ancestors of the Nama and other groups  
is an order of magnitude weaker than that observed between between western and eastern Africans (Table \ref{tab:migration-rates}).
All models infer relatively high gene flow between Ethiopia and western Africa
($m\approx2\times10^{-4},$ the constant proportion of migrant lineages per generation over 60ka).
We further find that Back-to-Africa gene flow at the beginning of the Holocene primarily
affected the ancestors of the Ethiopian agricultural populations, comprising
over half of their genetic ancestry, estimated to be 64--65\%. 
We observe significant gene flow from the Amhara and Oromo into the Nama, a signal which is likely a proxy for the movement of
eastern African caprid and cattle pastoralists \citep{Henn2008-xo,Breton2014-xb}, here estimated to constitute a 25\% ancestry
contribution 2,000 ya. While this gene flow is not apparent from the ADMIXTURE plot (Figure~\ref{fig:diversity}), the ancestry is likely grouped into the Khoe-San component which has drifted appreciably from its ancestry Eastern African source. Colonial period admixture from Europeans into the Nama
was estimated at 15\%, similar to proportions suggested by \texttt{ADMIXTURE}
(Figure~\ref{fig:diversity}).
